\documentclass[a4paper,12pt]{article}

% Fonts
\usepackage[T1]{fontenc}
\usepackage[scaled=1.0]{helvet}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{microtype}

% Page geometry
\usepackage[
  a4paper,
  top=25mm, bottom=25mm,
  left=25mm, right=25mm,
  headheight=14pt
]{geometry}

% Packages
\usepackage{ragged2e}
\usepackage{setspace}
\usepackage{parskip}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{mdframed}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows.meta, positioning, fit, backgrounds}

% Colors
\definecolor{sapblue}{RGB}{10, 110, 209}
\definecolor{darkgray}{RGB}{50, 54, 58}
\definecolor{lightgray}{RGB}{242, 242, 242}
\definecolor{accentgreen}{RGB}{16, 126, 62}
\definecolor{accentorange}{RGB}{233, 115, 12}
\definecolor{boxbg}{RGB}{235, 244, 255}

% Section formatting
\titleformat{\section}
  {\fontsize{15}{18}\bfseries\color{sapblue}}
  {\thesection.}{0.5em}{}
\titleformat{\subsection}
  {\fontsize{14}{17}\bfseries\color{darkgray}}
  {\thesubsection}{0.5em}{}
\titleformat{\subsubsection}
  {\fontsize{12}{15}\bfseries\color{darkgray}}
  {}{0em}{}

% Page style
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0.4pt}
\fancyhead[L]{\small\color{darkgray}Fleet Monitoring Application --- SAP BTP Capstone Project}
\fancyhead[R]{\small\color{darkgray}KIIT}
\fancyfoot[R]{\small\thepage}

% Hyperlinks
\hypersetup{
  colorlinks=true,
  linkcolor=sapblue,
  urlcolor=sapblue,
  pdfauthor={Arun Bhattacharya},
  pdftitle={Fleet Monitoring SAP BTP Capstone Project Report}
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}

\begin{document}
\justifying
\setstretch{1.15}

% Title Page
\thispagestyle{empty}

\begin{center}
  \vspace*{10mm}

  {\color{sapblue}\rule{\linewidth}{2pt}}
  \vspace{6mm}

  {\fontsize{22}{28}\bfseries\color{sapblue}
    Fleet Monitoring and Maintenance Automation\\[4pt]
    using SAP Cloud Application Programming Model}
  \vspace{4mm}

  {\fontsize{15}{20}\bfseries\color{darkgray} Capstone Project Report}
  \vspace{2mm}

  {\color{sapblue}\rule{\linewidth}{2pt}}
  \vspace{12mm}

  \begin{tabular}{rl}
    \textbf{Submitted By} & Arun Bhattacharya \\[4pt]
    \textbf{Roll Number}  & 23053266 \\[4pt]
    \textbf{College}      & Kalinga Institute of Industrial Technology \\[4pt]
    \textbf{Course}       & SAP BTP \\[4pt]
    \textbf{Program}      & SAP Business Technology Platform (BTP) \\[4pt]
    \textbf{Submitted On} & \today \\
  \end{tabular}

  \vspace{16mm}

  \begin{tikzpicture}[
      box/.style={
        rectangle, rounded corners=4pt,
        minimum width=2cm, minimum height=0.8cm,
        draw=sapblue, fill=boxbg, font=\small\bfseries, text=darkgray,
        align=center
      },
      arr/.style={-{Stealth[length=5pt]}, thick, color=sapblue}
  ]
    \node[box] (dev)  {Register\\Device};
    \node[box] (tel)  [right=0.6cm of dev] {Ingest\\Telemetry};
    \node[box] (alt)  [right=0.6cm of tel] {Generate\\Alert};
    \node[box] (wo)   [right=0.6cm of alt] {Create\\Work Order};
    \node[box] (done) [right=0.6cm of wo] {Assign \&\\Complete};

    \draw[arr] (dev)  -- (tel);
    \draw[arr] (tel)  -- (alt);
    \draw[arr] (alt)  -- (wo);
    \draw[arr] (wo)   -- (done);
  \end{tikzpicture}

  \vspace{6mm}
  {\small\color{darkgray}\itshape
    ``Monitoring fleet health in real time and converting abnormal telemetry into actionable maintenance workflows''}
\end{center}

\newpage
\setcounter{page}{1}

\section{Problem Statement}

In modern fleet operations, organizations rely on connected devices and sensors to monitor the health of vehicles, engines, and field assets. However, telemetry data is often collected separately from maintenance operations. This leads to multiple operational issues:

\begin{itemize}[leftmargin=1.5em, itemsep=3pt]
  \item Telemetry data is stored but not converted into actionable maintenance tasks.
  \item Operators do not have a single dashboard to monitor devices, alerts, and work orders.
  \item Manual alert handling causes delays in maintenance response.
  \item Work orders may be duplicated or lost when alerts are handled informally.
  \item There is limited visibility into how many devices are active, how many alerts exist, and how many maintenance jobs are still open.
\end{itemize}

The objective of this project is to build a cloud-native \textbf{Fleet Monitoring and Maintenance Automation} application on \textbf{SAP BTP} using the \textbf{SAP Cloud Application Programming Model (CAP)}. The system should accept telemetry readings, detect threshold breaches, create alerts, generate work orders, support technician assignment and completion, and expose the full flow through OData services and a dashboard UI.

\section{Solution and Features}

\subsection{Solution Overview}

The implemented application models the complete operational flow for fleet monitoring. A device is first registered in the system. Telemetry readings are then ingested for that device. When the value crosses a threshold, an alert is created automatically and a corresponding work order is opened. The work order can then be assigned to a technician and marked as completed after maintenance is done.

The backend is implemented using \textbf{SAP CAP with Node.js}. Local development uses \textbf{SQLite}, while the project structure remains portable for deployment on \textbf{SAP BTP}. The frontend is a lightweight HTML and JavaScript dashboard that provides a direct operational view of devices, alerts, and work orders.

\subsection{Key Features}

\begin{itemize}[leftmargin=1.5em, itemsep=4pt]
  \item \textbf{Device Registration} --- Users can register fleet devices with a unique device ID, device name, and model. Duplicate device IDs are rejected at the service layer.

  \item \textbf{Telemetry Ingestion} --- The application accepts telemetry readings such as temperature, pressure, or battery values through an unbound CAP action. Each telemetry event is persisted in the database.

  \item \textbf{Automatic Threshold Detection} --- Telemetry values are checked against a threshold. If the threshold is breached, the backend automatically creates an alert.

  \item \textbf{Alert-Driven Work Order Creation} --- On alert creation, the application triggers an in-process event flow and generates a maintenance work order. Duplicate work orders for the same alert are prevented.

  \item \textbf{Technician Management} --- Technicians can be maintained as a separate master entity and linked to work orders during assignment.

  \item \textbf{Work Order Lifecycle Management} --- Work orders support a clear lifecycle: \texttt{Open} to \texttt{Assigned} to \texttt{Completed}. Completion also records the closing timestamp.

  \item \textbf{Fleet Summary Reporting} --- A summary function groups work orders by status, enabling dashboard KPI views such as open jobs and completed jobs.

  \item \textbf{Browser Dashboard} --- A single-page dashboard provides live visibility into registered devices, generated alerts, and maintenance work orders.

  \item \textbf{Automated Integration Testing} --- The backend includes tests for registration, duplicate prevention, low telemetry, high telemetry, automatic alert creation, automatic work-order creation, manual work-order handling, assignment, completion, and fleet summary reporting.
\end{itemize}

\section{System Architecture}

\subsection{High-Level Architecture}

\begin{center}
\begin{tikzpicture}[
    box/.style={
      rectangle, rounded corners=4pt, draw=sapblue,
      minimum width=3cm, minimum height=1cm,
      align=center, font=\small\bfseries, fill=boxbg, text=darkgray
    },
    cloud/.style={
      box, fill=white, draw=accentgreen, text=accentgreen
    },
    arr/.style={-{Stealth[length=5pt]}, thick, color=sapblue}
]
  \node[box]   (ui)    {Browser UI\\(HTML / JS)};
  \node[box]   (cap)   [right=2cm of ui] {SAP CAP\\(Node.js)\\OData v4 Service};
  \node[box]   (db)    [right=2cm of cap] {SQLite\\(Local Dev)};
  \node[cloud] (btp)   [below=1.2cm of cap] {SAP BTP\\Cloud Foundry Ready};

  \draw[arr] (ui)  -- node[above,font=\scriptsize]{OData / JSON} (cap);
  \draw[arr] (cap) -- node[above,font=\scriptsize]{CDS Persistence} (db);
  \draw[arr,dashed] (cap) -- (btp);

  \begin{pgfonlayer}{background}
    \node[fill=lightgray, rounded corners=6pt, inner sep=10pt,
          fit=(cap)(db)(btp)] {};
  \end{pgfonlayer}
\end{tikzpicture}
\end{center}

\subsection{Backend Layer Design}

The project follows the standard CAP layered architecture:

\begin{center}
\begin{tabular}{>{\bfseries\color{sapblue}}p{3.5cm} p{9cm}}
\toprule
Layer & Responsibility \\
\midrule
\texttt{db/schema.cds}     & Defines entities, associations, and status fields for the fleet domain \\
\texttt{srv/o2c-service.cds} & Exposes the FleetService and declares actions/functions \\
\texttt{srv/o2c-service.js} & Implements business rules for registration, assignment, completion, and summary logic \\
\texttt{srv/telemetry.js}  & Encapsulates telemetry ingestion, threshold evaluation, and alert creation \\
\texttt{srv/event-handlers.js} & Handles AlertCreated events and work-order generation \\
\texttt{app/webapp/}       & Dashboard UI for device, alert, and work-order monitoring \\
\texttt{test/}             & Automated integration tests using Jest and \texttt{cds.test} \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Data Model}

The application is built around five main entities:

\begin{itemize}[leftmargin=1.5em, itemsep=2pt]
  \item \texttt{Devices} --- registered fleet devices or monitored assets
  \item \texttt{Telemetry} --- raw telemetry readings associated with devices
  \item \texttt{Alerts} --- generated when telemetry crosses a threshold
  \item \texttt{Technicians} --- maintenance personnel who can be assigned work
  \item \texttt{WorkOrders} --- maintenance tasks raised from alerts
\end{itemize}

Associations connect telemetry to devices, alerts to telemetry and devices, and work orders to alerts, devices, and technicians. This produces a traceable operational chain from signal detection to maintenance closure.

\section{Technology Stack}

\begin{center}
\begin{tabularx}{\linewidth}{>{\bfseries}l >{\raggedright\arraybackslash}X l}
\toprule
Component & Technology & Version \\
\midrule
CAP Framework & SAP Cloud Application Programming Model & 7.x \\
Runtime & Node.js & 18+ / 20 in dev shell \\
Data Modelling & CDS (Core Data Services) & --- \\
Service Protocol & OData v4 generated by CAP & v4 \\
Database (Dev) & SQLite & --- \\
Frontend & HTML5, CSS, Vanilla JavaScript & --- \\
Testing & Jest + \texttt{cds.test} & 29.x \\
Dependency Shell & Nix Flake Dev Environment & --- \\
Version Control & Git / GitHub & --- \\
Target Platform & SAP BTP Cloud Foundry & --- \\
\bottomrule
\end{tabularx}
\end{center}

\section{Process Flow Walkthrough}

The following process describes the operational workflow implemented in the project:

\begin{center}
\begin{tikzpicture}[
    state/.style={
      rectangle, rounded corners=6pt, draw=sapblue, fill=boxbg,
      minimum width=2.6cm, minimum height=1cm, align=center,
      font=\small\bfseries, text=darkgray
    },
    rule/.style={font=\scriptsize\itshape, color=accentorange, align=center, text width=2.4cm},
    arr/.style={-{Stealth[length=5pt]}, thick, color=sapblue}
]
  \node[state]              (device)     {Register\\Device};
  \node[state, right=1.6cm of device]   (telemetry) {Ingest\\Telemetry};
  \node[state, right=1.6cm of telemetry] (alert) {Create\\Alert};
  \node[state, right=1.6cm of alert] (work)  {Open\\Work Order};
  \node[state, right=1.6cm of work]  (complete)      {Assign /\\Complete};

  \draw[arr] (device) -- (telemetry);
  \draw[arr] (telemetry) -- (alert);
  \draw[arr] (alert) -- (work);
  \draw[arr] (work) -- (complete);

  \node[rule, above=0.3cm of telemetry] {Updates\\device lastSeen};
  \node[rule, above=0.3cm of alert] {Threshold\\evaluation};
  \node[rule, above=0.3cm of work] {Duplicate prevention\\for same alert};
  \node[rule, above=0.3cm of complete] {Technician assignment\\and closure};
\end{tikzpicture}
\end{center}

\textbf{Step-by-step implementation flow:}

\begin{enumerate}[leftmargin=1.8em, itemsep=4pt]
  \item \textbf{Register Device} --- A new fleet device is created using the \texttt{registerDevice} action. The backend validates uniqueness of the device ID.

  \item \textbf{Ingest Telemetry} --- A telemetry reading is submitted through the \texttt{ingestTelemetry} action with device, metric, value, and optional threshold information.

  \item \textbf{Alert Generation} --- The telemetry helper evaluates the numeric value. If the threshold is exceeded, an alert is stored automatically.

  \item \textbf{Automatic Work Order Creation} --- The alert triggers event handling logic, which creates a work order in \texttt{Open} state. If a work order already exists for that alert, the system reuses it instead of duplicating it.

  \item \textbf{Assignment and Completion} --- Operators can assign a technician to the work order and later mark it completed using bound OData actions on the \texttt{WorkOrders} entity.
\end{enumerate}

\section{Implemented APIs and Business Logic}

\subsection{Main Service Endpoints}

The FleetService exposes the following important operations:

\begin{itemize}[leftmargin=1.5em, itemsep=3pt]
  \item \texttt{POST /api/fleet/registerDevice}
  \item \texttt{POST /api/fleet/ingestTelemetry}
  \item \texttt{POST /api/fleet/createWorkOrder}
  \item \texttt{POST /api/fleet/WorkOrders(\{id\})/FleetService.assignWorkOrder}
  \item \texttt{POST /api/fleet/WorkOrders(\{id\})/FleetService.completeWorkOrder}
  \item \texttt{GET /api/fleet/getFleetSummary()}
\end{itemize}

\subsection{Implemented Business Rules}

\begin{itemize}[leftmargin=1.5em, itemsep=4pt]
  \item Device IDs must be unique.
  \item Telemetry ingestion updates the device's \texttt{lastSeen} timestamp.
  \item High telemetry values generate alerts automatically.
  \item Alerts create work orders automatically through event-driven handling.
  \item Duplicate work orders for the same alert are prevented.
  \item Work orders can be assigned only to valid technicians.
  \item Completion updates the work-order status and records closure time.
  \item Fleet summary aggregates work orders by status for dashboard KPIs.
\end{itemize}

\section{Frontend Dashboard}

The frontend is implemented as a lightweight browser dashboard in \texttt{app/webapp/index.html}. It contains:

\begin{itemize}[leftmargin=1.5em, itemsep=4pt]
  \item KPI cards for devices, active alerts, open work orders, and completed work orders
  \item A \textbf{Devices} tab to view registered devices and create new ones
  \item A telemetry ingestion panel for submitting metric readings
  \item An \textbf{Alerts} tab to monitor threshold breaches
  \item A \textbf{Work Orders} tab to track and complete maintenance tasks
\end{itemize}

The UI directly consumes the CAP OData service and reflects backend state changes immediately after telemetry ingestion and work-order completion.

\section{Testing and Validation}

To validate correctness, the project contains an automated integration test suite. The tests are executed using \texttt{Jest} together with the CAP \texttt{cds.test} harness and an in-memory SQLite profile.

The current automated tests cover:

\begin{itemize}[leftmargin=1.5em, itemsep=3pt]
  \item successful device registration
  \item duplicate device rejection
  \item telemetry below threshold without alert creation
  \item telemetry above threshold with alert generation
  \item automatic work-order creation from alerts
  \item manual work-order creation without duplication
  \item technician assignment
  \item work-order completion
  \item fleet summary reporting
\end{itemize}

This test coverage ensures that both normal and exceptional flows are verified at the service level.

\section{Unique Points}

\begin{enumerate}[leftmargin=1.8em, itemsep=5pt]
  \item \textbf{Telemetry-to-Action Flow} --- The project does not stop at storing sensor data. It converts operational signals into alerts and then into maintenance work orders.

  \item \textbf{Event-Driven Logic Inside CAP} --- The application uses in-process event handling to react to alert creation and automate work-order generation, which makes the design extensible for future messaging integration.

  \item \textbf{Operational Dashboard Simplicity} --- A simple frontend is used instead of a large framework, allowing focus on backend CAP logic while still demonstrating a full working UI.

  \item \textbf{Local Reproducibility through Nix} --- The project is supported by a Nix flake development shell, which helps keep Node.js, npm, SQLite, and CAP tooling consistent.

  \item \textbf{Clear Domain Traceability} --- The data model provides a direct trace from device to telemetry to alert to work order to technician handling, which is useful for both monitoring and auditability.

  \item \textbf{Automated Integration Testing} --- The application includes a passing suite of isolated integration tests, demonstrating that the implemented workflow is not only visible in the UI but also verified in code.
\end{enumerate}

\section{Future Improvements}

\begin{itemize}[leftmargin=1.5em, itemsep=4pt]
  \item \textbf{SAP Event Mesh Integration} --- Publish alert events to SAP Event Mesh so that external worker services or downstream systems can react asynchronously.

  \item \textbf{Role-Based Access Control} --- Integrate XSUAA roles such as Operator, Technician, and Supervisor to secure different actions by user type.

  \item \textbf{Technician Assignment UI} --- Extend the dashboard to support selecting technicians directly from the browser instead of relying only on API actions.

  \item \textbf{Device Health Analytics} --- Add historical charts and trend analysis for telemetry values such as temperature and pressure over time.

  \item \textbf{Notification Integration} --- Trigger email or alert notifications when a critical alert or overdue work order is detected.

  \item \textbf{HANA Cloud Deployment} --- Move from SQLite-based local development to SAP HANA Cloud deployment for production-scale persistence.

  \item \textbf{Predictive Maintenance} --- Introduce scoring models or ML-based anomaly detection instead of fixed thresholds for generating alerts.
\end{itemize}

\section{Conclusion}

This project demonstrates a complete SAP CAP implementation for a fleet monitoring use case. It combines master data management, telemetry ingestion, threshold evaluation, alert generation, event-driven work-order automation, technician workflow handling, reporting, and browser-based visibility in one coherent application.

From an SAP BTP learning perspective, the project shows how CAP can be used not only for CRUD-based enterprise apps but also for operational monitoring scenarios that require business rules, events, and process automation. The result is a practical, extensible, and well-tested application that can serve as a base for more advanced fleet operations on SAP BTP.

\vspace{8mm}
\begin{mdframed}[backgroundcolor=lightgray, roundcorner=4pt, linewidth=0pt, innertopmargin=8pt, innerbottommargin=8pt]
\textbf{Student Name:} Arun Bhattacharya\\
\textbf{Roll Number:} 23053266\\
\textbf{College:} Kalinga Institute of Industrial Technology\\
\textbf{Course:} SAP BTP\\
\textbf{Submission Date:} \today
\end{mdframed}

\end{document}
